\documentclass[12pt,a4paper]{article}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
\usepackage{natbib}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{caption}

\begin{document}

\title{Supplementary Materials:\\ Bivariate ExOW-POLO Regression with Cure Fraction and Bayesian Variable Selection}
\author{Mohamad Alani}
\date{}
\maketitle

\section{Alternative Marginal Distribution Comparison}

Table S1 presents the WAIC comparison of the ExOW-POLO distribution against 
three alternative flexible marginal distributions, each fitted with a mixture 
cure component to the OHTS data.

\begin{table}[htbp]
\centering
\caption{WAIC comparison of marginal distributions with cure fraction.}
\label{tab:S1}
\begin{tabular}{lcc}
\toprule
\textbf{Marginal Distribution} & \textbf{Parameters} & \textbf{WAIC} \\
\midrule
ExOW-POLO (proposed) & 5 & 8{,}550.1 \\
Generalised gamma & 4 & 8{,}562.5 \\
Log-skew-normal & 3 & 8{,}579.8 \\
Generalised beta (type 2) & 4 & 8{,}571.3 \\
\bottomrule
\end{tabular}
\end{table}

The ExOW-POLO achieved the lowest WAIC, supporting its selection on empirical 
grounds. The difference relative to the next-best model (generalised gamma) 
was $\Delta\text{WAIC} = 12.4$.

\section{Full Posterior Correlation Matrices}

Table S2 presents the posterior correlation matrix for key model parameters 
under the full BEPRCF (M4).

\begin{table}[htbp]
\centering
\caption{Posterior correlation matrix for key BEPRCF parameters.}
\label{tab:S2}
\begin{tabular}{lccccc}
\toprule
& $\theta$ & $\pi_{11}$ & $\pi_{00}$ & $a$ & $b$ \\
\midrule
$\theta$ & 1.00 & & & & \\
$\pi_{11}$ & $-0.41$ & 1.00 & & & \\
$\pi_{00}$ & $0.18$ & $-0.72$ & 1.00 & & \\
$a$ & $-0.08$ & $0.22$ & $-0.15$ & 1.00 & \\
$b$ & $0.12$ & $-0.31$ & $0.24$ & $-0.45$ & 1.00 \\
$\beta$ (susceptible scale) & $-0.34$ & $0.09$ & $-0.11$ & $0.28$ & $-0.19$ \\
\bottomrule
\end{tabular}
\end{table}

The moderate negative correlation between $\theta$ and $\pi_{11}$ 
($\rho \approx -0.41$) is expected---stronger dependence among susceptibles 
reduces the need for a high cure fraction to explain the observed plateau. 
The weak correlation between $\theta$ and $\pi_{00}$ ($\rho \approx 0.18$) 
indicates that the model effectively distinguishes cure-related plateaus 
from dependence-induced concordance among failures.

\section{Complete Likelihood Expressions for All Censoring Patterns}

For patient $i$, let $(L_{i1}, R_{i1})$ and $(L_{i2}, R_{i2})$ denote the 
interval-censoring brackets for the left and right eyes, respectively. The 
bivariate likelihood contribution integrates over the four latent cure states:

\[
\mathcal{L}_i(\Psi) = \pi_{11,i} I_{11,i} + \pi_{10,i} I_{10,i} 
+ \pi_{01,i} I_{01,i} + \pi_{00,i} I_{00,i}.
\]

\subsection{State (1,1): Both Eyes Cured}

$I_{11,i} = 1$ for all censoring patterns, as cured eyes contribute no 
event probability.

\subsection{State (1,0): Left Eye Cured, Right Eye Susceptible}

\begin{itemize}
\item \textbf{Right eye interval-censored} ($0 < L_{i2} < R_{i2} < \infty$):
  $I_{10,i} = S_2(L_{i2}) - S_2(R_{i2})$
\item \textbf{Right eye right-censored} ($R_{i2} = \infty$):
  $I_{10,i} = S_2(L_{i2})$
\end{itemize}

\subsection{State (0,1): Left Eye Susceptible, Right Eye Cured}

\begin{itemize}
\item \textbf{Left eye interval-censored} ($0 < L_{i1} < R_{i1} < \infty$):
  $I_{01,i} = S_1(L_{i1}) - S_1(R_{i1})$
\item \textbf{Left eye right-censored} ($R_{i1} = \infty$):
  $I_{01,i} = S_1(L_{i1})$
\end{itemize}

\subsection{State (0,0): Both Eyes Susceptible}

Let $S_{12}(u,v) = (S_1(u)^{-\theta} + S_2(v)^{-\theta} - 1)^{-1/\theta}$ 
denote the Clayton survival copula.

\begin{itemize}
\item \textbf{Both eyes interval-censored}:
  \begin{align*}
  I_{00,i} &= S_{12}(L_{i1}, L_{i2}) - S_{12}(R_{i1}, L_{i2}) \\
           &\quad - S_{12}(L_{i1}, R_{i2}) + S_{12}(R_{i1}, R_{i2})
  \end{align*}
\item \textbf{Left eye interval-censored, right eye right-censored}:
  $I_{00,i} = S_{12}(L_{i1}, L_{i2}) - S_{12}(R_{i1}, L_{i2})$
\item \textbf{Left eye right-censored, right eye interval-censored}:
  $I_{00,i} = S_{12}(L_{i1}, L_{i2}) - S_{12}(L_{i1}, R_{i2})$
\item \textbf{Both eyes right-censored}:
  $I_{00,i} = S_{12}(L_{i1}, L_{i2})$
\end{itemize}

\section{Complete Sensitivity Analysis Results}

Table S3 presents the full comparison between the main BEPRCF model 
(assuming conditional independence of cure indicators) and the sensitivity 
model with shared cure frailty.

\begin{table}[htbp]
\centering
\caption{Full sensitivity analysis: main BEPRCF vs.\ cure frailty model.}
\label{tab:S3}
\begin{tabular}{lccc}
\toprule
\textbf{Parameter} & \textbf{Main BEPRCF} & \textbf{Cure Frailty} & \textbf{Difference} \\
\midrule
$\theta$ (copula) & 1.76 (1.16, 2.53) & 1.58 (1.02, 2.31) & $-0.18$ \\
$\pi_{11}$ (joint cure) & 0.31 (0.22, 0.41) & 0.34 (0.24, 0.45) & $+0.03$ \\
$\pi_{00}$ (joint susceptible) & 0.52 (0.41, 0.63) & 0.49 (0.38, 0.60) & $-0.03$ \\
$\gamma_\pi$ (treatment on cure) & 0.61 (0.29, 0.94) & 0.58 (0.26, 0.91) & $-0.03$ \\
Treatment OR for cure & 1.84 (1.34, 2.56) & 1.79 (1.30, 2.48) & $-0.05$ \\
$\sigma^2_u$ (cure frailty) & --- & 0.14 (0.02, 0.31) & --- \\
WAIC & 8{,}550.1 & 8{,}547.8 & $-2.3$ \\
\bottomrule
\end{tabular}
\end{table}

The estimated cure frailty variance $\hat{\sigma}^2_u = 0.14$ 
(95\%~CrI:~0.02,~0.31) indicates modest unobserved heterogeneity in cure 
propensity. Under the sensitivity model, the copula parameter $\theta$ 
decreased from 1.76 to 1.58, consistent with the expectation that under 
conditional independence, the copula partially absorbs residual cure 
dependence. However, the treatment effect on cure probability remained 
robust (odds ratio 1.79 vs.\ 1.84), and the WAIC difference of 2.3 units 
is negligible relative to the model complexity difference. We therefore 
present the more parsimonious BEPRCF as our primary model.

\section{Prior Sensitivity Analysis}

Table S4 presents the sensitivity of posterior estimates to the choice of 
LASSO hyperprior. We varied the Gamma shape parameter $r \in \{0.1, 1, 10\}$ 
in the prior $\lambda^2 \sim \text{Gamma}(r, 1)$.

\begin{table}[htbp]
\centering
\caption{Prior sensitivity analysis: effect of LASSO hyperprior.}
\label{tab:S4}
\begin{tabular}{lccc}
\toprule
\textbf{Parameter} & $r = 0.1$ (weak) & $r = 1$ (default) & $r = 10$ (strong) \\
\midrule
$\theta$ (copula) & 1.79 (1.20, 2.58) & 1.76 (1.16, 2.53) & 1.72 (1.12, 2.47) \\
$\pi_{11}$ (cure) & 0.32 (0.23, 0.43) & 0.31 (0.22, 0.41) & 0.29 (0.20, 0.39) \\
$\gamma_\pi$ (treatment) & 0.63 (0.31, 0.97) & 0.61 (0.29, 0.94) & 0.57 (0.25, 0.90) \\
Active covariates (mean) & 5.2 & 4.1 & 2.8 \\
\bottomrule
\end{tabular}
\end{table}

Key parameter estimates are stable across hyperprior choices, with the 
treatment effect on cure probability varying by at most 0.06 on the log-odds 
scale.

\section{Extended Simulation Results}

Table S5 presents the complete simulation results for all sample sizes 
($n \in \{200, 500, 1000, 2000\}$) under correct specification.

\begin{table}[htbp]
\centering
\caption{Complete simulation results under correct specification.}
\label{tab:S5}
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter} & $n = 200$ & $n = 500$ & $n = 1000$ & $n = 2000$ \\
\midrule
\multicolumn{5}{c}{\textit{Absolute Bias}} \\
\midrule
$\theta$ & 0.14 & 0.07 & 0.04 & 0.02 \\
$\pi_{11}$ & 0.06 & 0.03 & 0.02 & 0.01 \\
$\pi_{00}$ & 0.08 & 0.04 & 0.02 & 0.01 \\
$\gamma_\alpha$ (treatment) & 0.09 & 0.04 & 0.02 & 0.01 \\
$\gamma_\pi$ (treatment) & 0.12 & 0.06 & 0.03 & 0.02 \\
\midrule
\multicolumn{5}{c}{\textit{RMSE}} \\
\midrule
$\theta$ & 0.38 & 0.21 & 0.14 & 0.09 \\
$\pi_{11}$ & 0.11 & 0.06 & 0.04 & 0.02 \\
$\pi_{00}$ & 0.15 & 0.08 & 0.05 & 0.03 \\
$\gamma_\alpha$ (treatment) & 0.22 & 0.11 & 0.07 & 0.05 \\
$\gamma_\pi$ (treatment) & 0.27 & 0.14 & 0.09 & 0.06 \\
\bottomrule
\end{tabular}
\end{table}

\section{Effective Sample Size Diagnostics}

Table S6 reports the bulk and tail effective sample sizes for key parameters.

\begin{table}[htbp]
\centering
\caption{Effective sample sizes (OHTS analysis).}
\label{tab:S6}
\begin{tabular}{lcc}
\toprule
\textbf{Parameter} & \textbf{Bulk ESS} & \textbf{Tail ESS} \\
\midrule
$\theta$ (copula) & 3{,}847 & 2{,}934 \\
$a$ (global) & 4{,}521 & 3{,}672 \\
$b$ (global) & 3{,}214 & 2{,}456 \\
$\eta$ (global) & 4{,}891 & 3{,}912 \\
$\gamma_\pi$ (treatment) & 5{,}234 & 4{,}101 \\
$\pi_{11}$ (generated) & 4{,}012 & 3{,}245 \\
\bottomrule
\end{tabular}
\end{table}

All parameters exceed the recommended threshold of 400, confirming adequate 
posterior exploration.

\end{document}
